Three 40 Million Year Old Mini-Neptunes from Kepler, TESS, and Gaia

### 2022-03-30 papers/ms.tex
update ms: imaging

The adopted stellar parameters are listed in
Table~\ref{tab:starparams}.  The stellar surface gravity, radius,
mass, and density are found by interpolating against the MIST
isochrones \citep{choi_mesa_2016}.  The statistical uncertainties from
this technique mostly originate from the parallax uncertaintes; the
systematic uncertainties are taken to be the absolute difference
between the PARSEC \citep{bressan_parsec_2012} and MIST isochrones.
Reported uncertainties are a quadrature sum of the statistical and
systematic components.

@@

{\bf TODO verify continuum normalization}
Given the reddening-corrected color of the star this is
consistent(ish) with the Pleiades/NGC2516 based on my NGC2516 figure.
But it looks sub-IC2602 based on the lithium.png figure, which uses
the Randich2018 values.
It's pretty clearly super-field.
I really need to verify the continuum normalization.
COMPARE vs:
\citealt{randich_gaiaeso_2018}).  
\citet{berger_identifying_2018}

\paragraph{High-Resolution Imaging}
{\bf todo}

\subsection{KOI-7368}
\paragraph{Spectra}
For KOI-7368, we acquired a spectrum using the echelle spectrograph
(TRES; \citealt{furesz_tres_2008}) mounted at the Tillinghast 1.5m at
the Fred Lawrence Whipple Observatory on Mt. Hopkins, AZ.  The
spectrum was acquired on 2015 June 1.  The stellar parameter
classification pipeline for these spectra is described by
\citet{2021tsc2.confE.124B}.  It is based on the synthetic template
library originally constructed by \citet{buchhave_hatp16b_class_2010}.
The resulting stellar parameters ($T_{\rm eff}, \log g, R_\star$)
agreed with those from the cluster-isochrone method within
$1$-$\sigma$, though the effective temperature is more precise by a
factor of three.  Auxiliary parameters included the metallicity $[{\rm
Fe/H}]= -0.02 \pm 0.08$, the equatorial velocity $v\sin i = 20.21 \pm
0.50\,\mkms$, and the systemic velocity ${\rm RV}_{\rm sys} = -10.9
\pm 0.2\,\mkms$.  The Li 6708\AA\ EW measurement procedure yielded
${\rm EW}_{\rm Li} = 236^{+16}_{-14}$\,m\AA.

@@

%(e.g., Jenkins KSCI-19081-002 KPDH pp 129, or many other pages)
KOI-7913 appears to be a binary.  The north-west
primary\footnote{Relevant identifiers for the primary are KIC 8873450
= Gaia DR2/EDR3 2106235301785454208.  For the secondary, they are KIC
8873448 = Gaia DR2/EDR3 2106235301785453824.  } is approximately 0.5
magnitudes brighter than the south-east secondary in optical passbands.
The two stars are separated in Gaia EDR3 by $3\farcs54$ on-sky, and
have parallaxes consistent within $1$-$\sigma$ (the average is
$\varpi=3.66 \pm 0.01$\,mas).  This corresponds to an apparent on-sky
separation of $959 \pm 2$ au.  Gaia EDR3 quotes
$(\mu_{\alpha'},\mu_\delta)=(2.439\pm0.015, 1.009\pm 0.016)\,{\rm
mas}\,{\rm yr}^{-1}$ for the primary, and
$(\mu_{\alpha'},\mu_\delta)=(2.696\pm0.020, 0.650 \pm 0.021) \,{\rm
mas}\,{\rm yr}^{-1}$ for the secondary.  Since two stars were resolved
in the Kepler Input Catalog and are roughly one Kepler pixel apart, an
accurate crowding metric has already been applied in the NASA Ames
data products to correct the mean flux level
\citep{2017ksci.rept....6M}.  This is important for deriving accurate
transit depths.

@@

Regarding indicators of youth, the primary has a spectral type
$\approx$K6V, while the secondary is $\approx$M0V.  At $\approx$40
Myr, 
lithium 6708\,\AA\ absorption is not expected for the
secondary, but might be present for the primary 
\citep[{\it e.g.},][Figure~8]{soderblom_ages_2014}.
Conversely,  {\bf todo finish}
% TODO: make this figure?

@@

>>>>

The adopted stellar parameters are listed in
Table~\ref{tab:sysparams}.  The stellar surface gravity, radius,
mass, and density are found by interpolating against the MIST
isochrones \citep{choi_mesa_2016}.  The statistical uncertainties from
this technique mostly originate from the parallax uncertaintes; the
systematic uncertainties are taken to be the absolute difference
between the PARSEC \citep{bressan_parsec_2012} and MIST isochrones.
Reported uncertainties are a quadrature sum of the statistical and
systematic components.

@@

% {\bf TODO verify continuum normalization in Li EW measurement...}
% Given the reddening-corrected color of the star this is
% consistent(ish) with the Pleiades/NGC2516 based on my NGC2516 figure.
% But it looks sub-IC2602 based on the lithium.png figure, which uses
% the Randich2018 values.
% It's pretty clearly super-field.
% I really need to verify the continuum normalization.
% COMPARE vs:
% \citealt{randich_gaiaeso_2018}).  
% \citet{berger_identifying_2018}

\paragraph{High-Resolution Imaging}
% KOI-6186 & 58662.62 &   Kp     &  4 &   80.00 &  4.1 &  4.8 &  5.4 &  5.8 &  6.5 &  6.8 &  7.6 &  8.3 &  8.2 &  8.3 &             Petigura \\ % N2.20190628.53389
We acquired adaptive optics imaging of Kepler-1643 on the night of
2019 June 28 using the NIRC2 imager on Keck-II (PI: E.~Petigura).
Using the narrow camera (FOV = 10.2\arcsec), we obtained 4 images in
the $K'$ filter ($\lambda = 2.12\,\mu$m) with a total exposure time of
320\,s. We analyzed these data following \citet{kraus_impact_2016},
and determined the detection limits to visual companions by analyzing
the residuals after subtracting an empirical PSF template. 
This procedure yielded contrast limits of $\Delta K' = 4.1$ mag at
$\rho = 150$ mas, $\Delta K' = 5.8$ mag at $\rho = 300$ mas, and
$\Delta K' = 8.3$ mag at $\rho > 1000$ mas.

\subsection{KOI-7368}
\paragraph{Spectra}
For KOI-7368, we acquired a spectrum on 2015 June 1 using the echelle
spectrograph (TRES; \citealt{furesz_tres_2008}) mounted at the
Tillinghast 1.5m at the Fred Lawrence Whipple Observatory on Mt.
Hopkins, AZ.  The stellar parameter classification pipeline for the
TRES spectra has been described by \citet{2021tsc2.confE.124B}.  It is
based on the synthetic template library originally constructed by
\citet{buchhave_hatp16b_class_2010}.  The resulting stellar parameters
($T_{\rm eff}, \log g, R_\star$) agreed with those from the
cluster-isochrone method within $1$-$\sigma$, though the effective
temperature is more precise by a factor of three.  Auxiliary
spectroscopic parameters included the metallicity $[{\rm Fe/H}]= -0.02
\pm 0.08$, the equatorial velocity $v\sin i = 20.21 \pm 0.50\,\mkms$,
and the systemic velocity ${\rm RV}_{\rm sys} = -10.9 \pm 0.2\,\mkms$.
The Li 6708\AA\ EW measurement procedure yielded ${\rm EW}_{\rm Li} =
236^{+16}_{-14}$\,m\AA.

\paragraph{High-Resolution Imaging}
% KOI-7368 & 58646.57 &   Kp     &  4 &   80.00 &  5.2 &  5.8 &  6.4 &  6.7 &  7.1 &  7.5 &  8.1 &  8.7 &  8.7 &  8.8 &                Huber \\ % N2.20190612.49290
We acquired adaptive optics imaging of KOI-7368 on the night of 2019
June 12 using the NIRC2 imager on Keck-II (PI: D.~Huber).  The
observational configuration and reduction was identical as for
Kepler-1643.  No companions were detected, and the analysis of the
image residuals yielded contrast limits of $\Delta K' = 5.2$ mag at
$\rho = 150$ mas, $\Delta K' = 6.7$ mag at $\rho = 300$ mas, and
$\Delta K' = 8.7$ mag at $\rho > 1000$ mas.

@@

%(e.g., Jenkins KSCI-19081-002 KPDH pp 129, or many other pages)
KOI-7913 appears to be a binary.\footnote{Relevant identifiers for the
primary are KIC 8873450 = Gaia DR2/EDR3 2106235301785454208.  For the
secondary, they are KIC 8873448 = Gaia DR2/EDR3 2106235301785453824.}
The north-west primary is $\approx$0.5 magnitudes brighter than the
south-east secondary in optical passbands.  The two stars are
separated in Gaia EDR3 by $3\farcs54$ on-sky, and have parallaxes
consistent within $1$-$\sigma$ (with an average $\varpi=3.66 \pm
0.01$\,mas).  This corresponds to an apparent on-sky separation of
$959 \pm 2$ au.  Gaia EDR3 quotes
$(\mu_{\alpha'},\mu_\delta)=(2.439\pm0.015, 1.009\pm 0.016)\,{\rm
mas}\,{\rm yr}^{-1}$ for the primary, and
$(\mu_{\alpha'},\mu_\delta)=(2.696\pm0.020, 0.650 \pm 0.021) \,{\rm
mas}\,{\rm yr}^{-1}$ for the secondary.  Since two stars were resolved
in the Kepler Input Catalog and are roughly one Kepler pixel apart, an
accurate crowding metric has already been applied in the NASA Ames
data products to correct the mean flux level
\citep{2017ksci.rept....6M}.  This is important for deriving accurate
transit depths.

@@

Regarding indicators of youth, the primary has a spectral type
$\approx$K6V, while the secondary is $\approx$M0V.  At $\approx$40
Myr, lithium 6708\,\AA\ absorption is not expected for the secondary,
but might be present for the primary \citep[{\it
e.g.},][Figure~8]{soderblom_ages_2014}.  Conversely, H$\alpha$ is
expected to be in emission for for all M-dwarfs younger than
$\approx150$\,Myr \citep{kiman_calibration_2021}.

Turning to the actual data, we find {\bf X for lithium}.
For H$\alpha$, {\bf we see Y}.

@@

We acquired adaptive optics imaging of KOI-7913 on the night of 2020
Aug 27 using the NIRC2 imager on Keck-II (PI: D.~Huber).  The
observational configuration and reduction was identical as before.
The images showed KOI-7913 A, KOI-7913 B, and an additional faint star
$\approx0\farcs99$ due East of KOI-7913 B.  Applying the PSF-fitting
routines from \citet{kraus_impact_2016}, the tertiary star has a
separation $\rho = 4397 \pm 3$\,mas from the primary, at a position
angle $231.17^\circ \pm 0.02^\circ$, with a $\Delta K' = 6.97 \pm
0.04$.  While it is too faint to affect the interpretation of the KOI
itself, it would be amusing if the faint neighbor were also comoving
and young -- at the age of the system, it would have a mass roughly
between 10 and 15\,M$_{\rm Jup}$.  Additional imaging epochs will be
required to tell.
